---
title: "Week 4 Part 1- CIs and t-tests"
author: "Cali Pfleger"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## 1. Confidence Intervals 

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)

```

## 2. T-test (1- sample t-test)

- See a claim: mean otter length is 50 inches 

```{r}
otter_test <- t.test(x= otter_length, mu = 50)
otter_test

```


## 3. Two-sample t-test

```{r}
deser_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42,26, 29, 31)

t.test(x= deser_bighorns, y = sierra_bighorns)
```


## END PART 1

## Part 2: Two-sample t-test 

## 1. Create subset of suv and compact cars

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))
```

## 2. Exploratory data  visualization using ggplot

# -Exploratory histograms:

```{r}
ggplot( data = compact_suv, aes(x= cty)) +
  geom_histogram(bins =15) +
  facet_wrap(~class)
```

## 3. Quantile-quantile plot (qq plot)
- compare my sample to theoretical to see the distribution (?)


```{r}
ggplot(data = compact_suv, aes(sample= cty)) +
  geom_qq() +
  facet_wrap(~class)
```


## 4. Descriptive Statistics


```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(mean_city = mean(cty), 
            sd_city= sd(cty),
            n = n()) #calculate # of observations in each group 
```

## 5. 2-sample t-test

- first create vectors containg observations for each sample (city gas mileage)

- pull will extract a single colun and store it as a vector

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)

t.test(x= compact_sample, suv_sample)
```




















